%----------------------------------------------------------------------------------------
% PUBLIC ENGAGEMENT 
%----------------------------------------------------------------------------------------

\section{Public Engagement}
\cventry{2018}{Engaging Scientists in Policy and Advocacy}{}{}{}{Voluteer for
``Ask a Scientist at Art Fair'', where I spoke to adults interested in science at
a large local event in an informal setting.}
\cventry{2018}{\href{https://www.skypeascientist.com}{Skype a
Scientist [Link]}}{}{}{}{Volunteered for the Skype a Scientist program, where I skyped
into high school classrooms to talk about science, becoming a
scientist, and other topics.  More information on my blog,
\href{https://www.mcallister.science/skype-a-scientist}{here. [Link]}}
\cventry{2017}{\href{https://annarbor.nerdnite.com}{Nerd Nite [Link]} Ann Arbor
Talk}{}{}{}{Gave a 20 minute talk about my research at
a local bar to an audience of mostly non-scientists. A recording is
available at: \href{https://aadl.org/node/353283}{LED Light Bulbs: Why Do They
Cost an Arm and a Leg? [Link]}}
\cventry{2013-2016}{American Society for Engineering Education}{}{}{}{Organized
and ran a table at K-Grams Kid's Fair --  an elementary school visit to University
of Michigan. At the table, I helped demonstrate some concepts of signal analysis by using a
laser to transmit music through open air.}
\cventry{2008-2012}{Society of Physics Students}{}{}{}{Organized
and ran multiple outreach events at local schools and on campus. A large project
that I was involved with was organizing a full-day program on light and solar cells
for the Harlem Academy's visit to Rensselaer with my advisor, Peter Persans.}
