%----------------------------------------------------------------------------------------
% RESEARCH INTERESTS
% You can add keywords here if you think it's appropriate. Collaborators may also appear here.
%------------------------------------------------------------------------------------------

\subsubsection{Interests} 
I develop and apply computational methods to study materials
used in LEDs. LED bulbs are still very expensive compared to bulbs like
incandescents and compact-fluorescents. I am trying to reduce that cost using
supercomputers. My methods can predict properties that these materials have
before an experimentalists has to go through the expensive and time consuming
process of making the material in the lab. That time and money can be saved by
my calculations, leading to faster discovery of materials that have
desireable properties. With my calculations, I hope to find new materials that
can be realized in the lab that will lead to more efficient and cheaper LEDs. \\

I also am focused on communicating science, both to technical and lay-audiences.
This is just as important as doing good science. If no one understands what I am
trying to do, I won't be able to get the support I need to do research. To gain
experience with this, I have been involved with various K-12 and adult public
engagement events. I have taught technical writing to other graduate students. I
have written and edited with Michigan Science Writers. And I have sought out
specific training to improve my skills, like the RELATE workshop series at the
University of Michigan and the ComSciCon Workshop in Chicago.
