%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,letter,sans,final,colorlinks,linkcolor=blue]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvcolor{blue}
\moderncvstyle[left]{classic}

\usepackage{fontawesome}
\usepackage{multirow, multicol}

% to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}
% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...


% personal data
\name{Andrew}{McAllister}
\title{Doctorate in Applied Physics, Science Communicator}
\address{3559 Burbank Drive}{Ann Arbor, MI 48105}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{732-275-5051}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{mcala@umich.edu}                               % optional, remove / comment the line if not wanted
\homepage{www.mcallister.science}                         % optional, remove / comment the line if not wanted
\social[twitter]{McAllisterSci}                             % optional, remove / comment the line if not wanted
\social[linkedin]{McAllisterSci}                        % optional, remove / comment the line if not wanted
%\social[github]{mcala}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
%\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\definecolor{links}{HTML}{0000FF}
\hypersetup{urlcolor=links}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\vspace{-10cm}
\makecvtitle
\vspace{-1.3cm}

\input{./parts/summary.tex}
\input{./parts/education.tex}
\input{./parts/writing.tex}
\input{./parts/training.tex}
\input{./parts/awards.tex}
\input{./parts/engagement.tex}
\input{./parts/leadership.tex}
\input{./parts/memberships.tex}
%\input{./parts/teaching.tex}
%\input{./parts/work.tex}
%\input{./parts/skills.tex}
%\input{./parts/combined.tex}
%\input{./parts/publications.tex}
%\input{./parts/presentations.tex}
%\input{./parts/classes.tex}
%\input{./parts/funding.tex}
%\input{./parts/mentoring.tex}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\clearpage
%%%-----       letter       ---------------------------------------------------------
%% recipient data

\pagenumbering{gobble}
\recipient{American Association for the Advancement of Science}{1200 New York Avenue NW \\ Washington, D.C. 20005}
\date{August 6th, 2018}
\opening{Dear hiring team,}
\closing{Sincerely,}
\enclosure[Attached]{Resume (online), three writing samples (following this letter)}
\makelettertitle

Communicating why science is important, interesting and relevant to society is vital to have continued support for science. By making complex subjects understandable to non-experts, there can be two-way dialogue between the experts and non-experts, facilitating democratic science that is for the public good. I am excited to bring my skills and experiences to the AAAS and help write about the ways that science is a part of everyone’s life as a Science News Writer Intern (Requisition ID : 1269). My PhD has given me communicative, technical and social abilities that would be valuable for this position.

Throughout my scientific training, I have sought out experiences to develop and practice my communication skills in various mediums and to various audiences. My experience with the Researchers Expanding Lay-Audience Teaching and Engagement (RELATE) program at the University of Michigan was particularly productive. Over 3 months I worked on crafting messages and narratives, considering different audiences and making visual aids. Ultimately these experiences lead to a YouTube video and a talk at a local bar about my research.

My attached writing samples will show my experience in writing for a broad audience. But I also have editing experiences that speaks to these skills. As the senior editor of the Students of Applied Physics project, where I work with PhD students to develop understandable and engaging articles about research in the applied physics department. These students have various prior experiences writing for a broader audience, and helping them craft their own narratives and get their articles together has been valuable.

A vital part of completing my PhD was learning how to quickly find, read, and see the big picture behind modern research.This skill is valuable as a science news writer as I work to report and understand scientific results quickly in a way that engages a diverse audience. The ability to understand other scientists in writing extends to speaking to scientists in-person. As a computational researcher, I frequently collaborate with other researchers from different fields. Being able to ask questions and understand the science that they are studying is necessary for a fruitful collaboration and would also be relevant to this position.

Over the past year, in my spare time, I have published my writing on science for a general audience at the University of Michigan, Harvard’s Science in the News Blog, and on my personal blog. Working on publicizing my blog has also given me an (admittedly small) set of experience with working on social media. Given the opportunity to put my main interest of science writing first, rather than on the side, is what really excites me about finishing my PhD and moving forward with my career. I am excited to discuss my skills and experiences with you and can be reached at mcala@umich.edu or at 732-275-5051.

\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
